Conflict-Free Vertex Coloring Of Planar Graphs

### 2017-03-21 paper/paper.tex
Adding some citations
Adding some stuff on planar graphs

Imagine we have a set of readers, $R$. Suppose they all are assigned the same frequency. We would like to schedule each reader $r \in R$ a time slot $t(r)$ where the reader $r$ will be active. We have a set of tags $P$ (i.e. automobile RFID chips). We can say that $P$ is read by our schedule if for every tag $p \in P$, there is at least one reader $r \in R$ and a time $t$ such that $p$ is read by $r$ at time $t$. We want to minimize the total time slots used by the schedule. This can be accomplished by modeling the situation as a conflict-free coloring problem. Again, we aim to find the minimum number of colors needed.

@@

\subsection{Iterated Elimination of Distance-3-Sets}

@@

\section{CF Coloring of Planar Graphs}

\section{Complexity of Coloring CF Graphs}

>>>>

Imagine we have a set of readers, $R$. Suppose they all are assigned the same frequency. We would like to schedule each reader $r \in R$ a time slot $t(r)$ where the reader $r$ will be active. We have a set of tags $P$ (i.e. automobile RFID chips). We can say that $P$ is read by our schedule if for every tag $p \in P$, there is at least one reader $r \in R$ and a time $t$ such that $p$ is read by $r$ at time $t$. We want to minimize the total time slots used by the schedule. This can be accomplished by modeling the situation as a conflict-free coloring problem. Again, we aim to find the minimum number of colors needed. \cite{cheilaris2014strong, smorodinsky2013conflict}

@@

\subsection{Iterated Elimination of Distance-3-Sets}
The iterated elimination of distance-3-sets algorithm is a polynomial time heuristic for generating a conflict-free k-coloring of general graphs that meet the criterion in theorem \ref{thm:criterion}.

@@

\todo[inline]{Create and go through an example of this algorithm}

\section{CF Coloring of Planar Graphs}
Conflict-free coloring has some interesting properties when we limit the input graph to be a planar graph. Recall that a graph is planar if it can be drawn on the plane in such a way that its edge intersect only at their endpoints.

\subsection{CF Four Color Theorem}
Recall the map of the USA example given in the introduction. This is an example of a planar graph and has a famous theorem associated with it. We present this in theorem \ref{thm:four}. This theorem has been proved by multiple groups. The proof by computer that is widely accepted today can be found in \cite{robertson1997four}.

\begin{theorem} \label{thm:four}
Every loopless planar graph admits a vertex coloring with at most four distinct colors
\end{theorem}

The conflict-free variation of this theorem is quite simple. We present this in theorem \ref{thm:four-cf}. It is given and proven in \cite{abel2017three}.

\begin{theorem} \label{thm:four-cf}
Every loopless planar graph admits a conflict-free coloring with at most three distinct colors
\end{theorem}

This can be easily thought of intuitively as we can take any four-colored planar graph and uncolor all vertices of a chosen color. This leaves us with some vertices uncolored and vertices colored with 3 other colors. Thus, it is always true that a planar graph can be conflict-free colored with 3 colors or less. An example of this is shown in figure \ref{fig:four}.

\begin{figure}[h]
	\centering
	\includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/four.pdf}
	\caption{A vertex coloring and CF coloring, respectively}\label{fig:four}
\end{figure}

\todo[inline]{Go into more methods for planar graphs}
